---
title: "Simulation Result 2: U[1,4], all the parameters"
author: "Yi"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
options(knitr.kable.NA = '', digits = 4)
library(knitr)
library(kableExtra)
library(tidyverse)
library(wrapr)
library(ggplot2)
library(gridExtra)

rm(list = ls())
load("a-calc/beta1_pts50_150.RData")

```

\begin{equation*}
\begin{aligned}
\mathrm{Biomarker1}:\tilde X = 
\left\{\begin{matrix}
`r set$mk1[1]`+`r set$mk1[3]`e &\mathrm{if~} \tilde T\le2
\\ 
`r set$mk1[2]`+`r set$mk1[4]`e &\mathrm{if~} \tilde T>2
\end{matrix}\right.
\end{aligned} 
\end{equation*}
\begin{equation*}
\begin{aligned}
\mathrm{Biomarker2}:\tilde X = 
\left\{\begin{matrix}
`r set$mk2[1]`+`r set$mk2[3]`e &\mathrm{if~} \tilde T\le2
\\ 
`r set$mk2[2]`+`r set$mk2[4]`e &\mathrm{if~} \tilde T>2
\end{matrix}\right.
\end{aligned} 
\end{equation*}


```{r, include=FALSE}
mtd.name <- c("BNM.P", "TNM.P", paste0(rep(c("BNM.O", "TNM.O", "SA.o", "SA.p", "SA.n"),3),rep(c(7,5,3), each=5)))
dimname.sauc <- list(NULL, mtd.name)
dimname.par <- list(
  c("mu1", "mu2", "mu3", "tau1", "tau2", "tau3", "rho1", "rho2", "rho3", "sauc", "conv",
    "beta", "alpha.p", "SN", "p.est", "p.est.a", "p.est.b"), 
  mtd.name)
dimname.sauc.med <- list(mtd.name, 
                         c("Median (Q1, Q3)"))
dimname.sauc.msd <- list(mtd.name, 
                         c("Mean (SD)"))

ave_mat <- function(path = "S200/ptdis1_HR2.RData", only.conv = TRUE){ 

  load(path)
  if(only.conv){
    
    nconv <- DATA[11,]!=0
    DATA[1:10, nconv] <- NA
    
  }
  # ncv <- sum(!complete.cases(DATA[1,]))
  # 
  sauc.val <- colMeans(matrix(DATA[10, ], ncol = 17, dimnames = dimname.sauc), na.rm=TRUE)*100
  # 
  # ## convergence rate
  cv   <- matrix(DATA[11,], ncol = 17, byrow = T)
  cv.sum  <- sapply(1:17, function(i) sum(1-cv[,i], na.rm = TRUE)/10)
  
  # MED pf pars
  dim(DATA) <- c(17, 17, dim(DATA)[2]/17)
  med <- apply(DATA, 1:2, function(x) median(x, na.rm = TRUE))
  med[11, ] <- cv.sum
  # med[10, ] <- med[10, ] * 100 
  med[10, ] <- (med[10, ]-  med[10, 1])*100
  dimnames(med) <- dimname.par
  # q1  <- apply(DATA, 1:2, function(x) quantile(x, probs = 0.25, na.rm = TRUE))
  # q3  <- apply(DATA, 1:2, function(x) quantile(x, probs = 0.75, na.rm = TRUE))
  # 
  # mean <- apply(DATA, 1:2, function(x) mean(x, na.rm = TRUE))
  # sd   <- apply(DATA, 1:2, function(x) sd(x, na.rm = TRUE))

  
  return(list(med=med, sauc.val=sauc.val))
}
```




```{r, include=FALSE}
## PT DISTRIBUTION 1 ----

## OBJECT NAME EXAMPLE: N20.D1.HR1.P0.8

for(S in c("S200", "S70")){
	
	for(ptdist in 1){
		
		for(HR in 1:2){
		  
		  for(ptdist in 1:2){
				
				assign(paste0(S, ".D", ptdist, ".HR", HR), 
											ave_mat(paste0(S, "/ptdis", ptdist, "_HR", HR, ".RData")) )
		  }
		}
	}
}


```


## S, SAUC, Conv Table

```{r}

rbind.data.frame(
  S70.D1.HR1$med[c(14, 10, 11),c("BNM.P", "BNM.O7", "SA.o7", "BNM.O5", "SA.o5", "BNM.O3", "SA.o3")],
  S200.D1.HR1$med[c(14, 10, 11),c("BNM.P", "BNM.O7", "SA.o7", "BNM.O5", "SA.o5", "BNM.O3", "SA.o3")]
  )%>%kbl(format = "html",caption = "D1, HR1")%>% 
  kable_styling("striped", position = "left", font_size = 12)


rbind.data.frame(
  S70.D1.HR2$med[c(14, 10, 11),c("BNM.P", "BNM.O7", "SA.o7", "BNM.O5", "SA.o5", "BNM.O3", "SA.o3")],
  S200.D1.HR2$med[c(14, 10, 11),c("BNM.P", "BNM.O7", "SA.o7", "BNM.O5", "SA.o5", "BNM.O3", "SA.o3")]
  )%>%kbl(format = "html",caption = "D1, HR2")%>% 
  kable_styling("striped", position = "left", font_size = 12)


rbind.data.frame(
  S70.D2.HR1$med[c(14, 10, 11),c("BNM.P", "BNM.O7", "SA.o7", "BNM.O5", "SA.o5", "BNM.O3", "SA.o3")],
  S200.D2.HR1$med[c(14, 10, 11),c("BNM.P", "BNM.O7", "SA.o7", "BNM.O5", "SA.o5", "BNM.O3", "SA.o3")]
  )%>%kbl(format = "html",caption = "D2, HR1")%>% 
  kable_styling("striped", position = "left", font_size = 12)


rbind.data.frame(
  S70.D2.HR2$med[c(14, 10, 11),c("BNM.P", "BNM.O7", "SA.o7", "BNM.O5", "SA.o5", "BNM.O3", "SA.o3")],
  S200.D2.HR2$med[c(14, 10, 11),c("BNM.P", "BNM.O7", "SA.o7", "BNM.O5", "SA.o5", "BNM.O3", "SA.o3")]
  )%>%kbl(format = "html",caption = "D2, HR2")%>% 
  kable_styling("striped", position = "left", font_size = 12)

```


## All par Table

```{r}

rbind.data.frame(
  S70.D1.HR1$med,
  S200.D1.HR1$med
  )%>%kbl(format = "html",caption = "D1, HR1") %>% 
  kable_styling("striped", position = "left", font_size = 12)



rbind.data.frame(
  S70.D1.HR2$med,
  S200.D1.HR2$med
  )%>%kbl(format = "html",caption = "D1, HR2")%>% 
  kable_styling("striped", position = "left", font_size = 12)


rbind.data.frame(
  S70.D2.HR1$med,
  S200.D2.HR1$med
  )%>%kbl(format = "html",caption = "D2, HR1")%>% 
  kable_styling("striped", position = "left", font_size = 12)


rbind.data.frame(
  S70.D2.HR2$med,
  S200.D2.HR2$med
  )%>%kbl(format = "html",caption = "D2, HR2")%>% 
  kable_styling("striped", position = "left", font_size = 12)

```


