---
title: 'Simulation Result for Manuscript'
author: "Yi"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(knitr)
library(kableExtra)
library(tidyverse)

# library(ggpubr)
rm(list = ls())
save.tex <- T
load("exp0.2/a-calc/beta1_pts50_150.RData")

```

\begin{equation*}
\begin{aligned}
\mathrm{Biomarker1}:\tilde X = 
\left\{\begin{matrix}
`r set$mk1[1]`+`r set$mk1[3]`e &\mathrm{if~} \tilde T\le2
\\ 
`r set$mk1[2]`+`r set$mk1[4]`e &\mathrm{if~} \tilde T>2
\end{matrix}\right.
\end{aligned} 
\end{equation*}
\begin{equation*}
\begin{aligned}
\mathrm{Biomarker2}:\tilde X = 
\left\{\begin{matrix}
`r set$mk2[1]`+`r set$mk2[3]`e &\mathrm{if~} \tilde T\le2
\\ 
`r set$mk2[2]`+`r set$mk2[4]`e &\mathrm{if~} \tilde T>2
\end{matrix}\right.
\end{aligned} 
\end{equation*}



```{r}

alpha <- NULL
load("exp0.2/a-calc/beta1_pts50_150.RData")
alpha <- rbind(alpha, set$alpha1)
load("exp0.2/a-calc/beta1_pts50_300.RData")
alpha <- rbind(alpha, set$alpha1)

load("exp0.2/a-calc/beta1_pts50_150.RData")
alpha <- rbind(alpha, set$alpha2)
load("exp0.2/a-calc/beta1_pts50_300.RData")
alpha <- rbind(alpha, set$alpha2)

load("U14/a-calc/beta1_pts50_150.RData")
alpha <- rbind(alpha, set$alpha1)
load("U14/a-calc/beta1_pts50_300.RData")
alpha <- rbind(alpha, set$alpha1)

load("U14/a-calc/beta1_pts50_150.RData")
alpha <- rbind(alpha, set$alpha2)
load("U14/a-calc/beta1_pts50_300.RData")
alpha <- rbind(alpha, set$alpha2)

set.tab <- data.frame(
	CD = c("$Exp(0.2)$", rep(NA,3), "$U(1,4)$", rep(NA,3)),
	MK = rep(c(1,NA, 2, NA), 2),
	PD = rep(c("$U(50,150)$", "$U(50,300)$"), 4),
	beta = rep(1,8),
	alpha
)

rownames(set.tab) <- NULL
colnames(set.tab) <- c("Censoring", "Biomarker", "Subjects", 
																							"$\\beta$", "$\\alpha_{0.7}$", "$\\alpha_{0.5}$", "$\\alpha_{0.3}$")

set.tab%>%
  kbl(
    caption="Scenarios of simulation",
    format ="latex",
    longtable = F, 
    booktabs = T,
    linesep = c(rep('',3), '\\addlinespace'),
    align = "r",
    position = "!htb",
    escape = FALSE,
    label = "set")
```




```{r func1, include=FALSE}

## FUNCTION FOR CREATING OBJECT

mtd.name <- c("BNM.P", "TNM.P", paste0(rep(c("BNM.O", "TNM.O", "SA.o", "SA.p", "SA.n"),3),rep(c(7,5,3), each=5)))
dimname.sauc <- list("SAUC", mtd.name)
dimname.cr <- list("CR", mtd.name)
dimname.sn <- list("S", mtd.name)

result_list <- function(path = "exp0.2/S70/ptdis1_HR2.RData", only.conv = T){ 

  load(path)
  if(only.conv){
    
    nconv <- DATA[11,]!=0
    DATA[1:10, nconv] <- NA
    
  }
  
  ##
  SN <- colMeans(matrix(DATA[14, ], ncol = 17, byrow = TRUE), na.rm=TRUE)
  dim(SN) <- c(1, 17)
  dimnames(SN) <- dimname.sn
  SS <- sprintf("%.f", SN)
  
  
  ## convergence rate
  cr  <- round(colMeans(matrix(DATA[11, ]==0, ncol = 17, byrow = TRUE), na.rm=TRUE)*100,2)
  dim(cr) <- c(1, 17)
  dimnames(cr) <- dimname.cr
  
  # MED pf sauc
  sauc <- matrix(DATA[10,], ncol = 17, byrow = TRUE)
  succ <- nrow(sauc)/10
  
  med <- apply(sauc, 2, function(x) median(x, na.rm = TRUE))*100
  # med <- med-med[1]
  q1  <- apply(sauc, 2, function(x) quantile(x, probs = 0.25, na.rm = TRUE))*100
  q3  <- apply(sauc, 2, function(x) quantile(x, probs = 0.75, na.rm = TRUE))*100
  
  sauc.med.q13 <- sprintf("%.2f (%.2f, %.2f)", med, q1, q3)
  dim(sauc.med.q13) <- c(1, 17)
  dimnames(sauc.med.q13) <- dimname.sauc
  
  
  
  res <- t(rbind(SS, sauc.med.q13, cr)[,c(1,3,5,8,10,13,15)])
  res[-1,1] <- ""
  
  return(res)
}
```




```{r, include=FALSE}

## CREATE OBJECT
## OBJECT NAME EXAMPLE: N20.D1.HR1.P0.8

for(folder in c("exp0.2/", "U14/")){
	
	for(S in c("S70", "S200")){
	
	for(ptdist in 1:2){
		
		for(HR in 1:2){
			
				if (folder=="exp0.2/") fd <- "F1." else fd <- "F2."
				assign(paste0(fd, S, ".D", ptdist, ".HR", HR), 
											result_list(paste0(folder, S, "/ptdis", ptdist, "_HR", HR, ".RData")) )
		}
	}
}
	
}


```




```{r}

## FUNCTION FOR CREATING SMALL TABLES

sauc11 <- rbind.data.frame(
	F1.S70.D1.HR1, 
	F1.S200.D1.HR1
	)
colnames(sauc11) <- c("S", c("Median (Q1, Q3)", "CR"))

sauc12 <- rbind.data.frame(
	F1.S70.D2.HR1, 
	F1.S200.D2.HR1
	)
colnames(sauc12) <- c("S", c("Median (Q1, Q3)", "CR"))

sauc21 <- rbind.data.frame(
	F1.S70.D1.HR2, 
	F1.S200.D1.HR2
	)
colnames(sauc21) <- c("S", c("Median (Q1, Q3)", "CR"))

sauc22 <- rbind.data.frame(
	F1.S70.D2.HR2, 
	F1.S200.D2.HR2
	)
colnames(sauc22) <- c("S", c("Median (Q1, Q3)", "CR"))


tab <- rbind(
  cbind(sauc11, sauc21), 
  cbind(sauc12, sauc22))

medq <- tab[,-c(1,4)]
S <- tab[,1]
Patients <- c("50-150", rep("", 13), "50-300", rep("", 13))
Methods <- rep(c(
  "HZ$_P$", 
  "HZ$_O$","Prop$_{(0.7)}$",
  "HZ$_O$","Prop$_{(0.5)}$",
  "HZ$_O$","Prop$_{(0.3)}$"),4)
P <- rep(c("", "0.7", "", "0.5", "", "0.3", ""),4)
tab1 <- cbind(
  Patients, S, P, Methods, medq
)
  
colnames(tab1) <- c("Patients","S", "$p$", "Methods", 
                    "Median (Q1, Q3)", "CR", "Median (Q1, Q3)", "CR")
rownames(tab1) <- NULL

ftn <- "
  Patients denote the range of the number of patients.
  $S$ denotes the number of the population studies.
  $p$ denotes the approximate proportion of the published studies among the population.
	Median with 25th and 75th empirical quartiles (Q1, Q3) of the SAUC at $t=2$ are reported. 
	CR denotes the proportion of successfully convergenced estimates among 1000 repetition.
	HZ$_P$ denotes the HZ model using the population studies; 
	HZ$_O$ denotes the HZ model using only the corresponding numbers of published studies;
	Prop$_{(p)}$ denotes the proposed sensitivity analysis method given $p$.
	All the entries are multiplied by 100."

if (save.tex) sink("TB-SAUC-EXP.tex")
tab1 %>%
  kbl(
    caption="Summary of the estimated SAUC(2) when the true censoring is distributed as $Exp(0.2)$.",
    format = "latex",
    longtable = F, 
    booktabs = T,
    align = "r",
    position = "!htb",
    linesep = c(rep('',6), '\\addlinespace'),
    escape = FALSE,
    label = "tab2",) %>%
  add_header_above(c(rep("",4), "Biomarker1"=2, "Biomarker2"=2),escape = FALSE) %>%
  footnote(general = ftn, 
   escape = FALSE, 
			threeparttable = TRUE,  
			general_title = "")
if (save.tex) sink()


## FUNCTION FOR CREATING SMALL TABLES

sauc11 <- rbind.data.frame(
	F2.S70.D1.HR1, 
	F2.S200.D1.HR1
	)
colnames(sauc11) <- c("S", c("Median (Q1, Q3)", "CR"))

sauc12 <- rbind.data.frame(
	F2.S70.D2.HR1, 
	F2.S200.D2.HR1
	)
colnames(sauc12) <- c("S", c("Median (Q1, Q3)", "CR"))

sauc21 <- rbind.data.frame(
	F2.S70.D1.HR2, 
	F2.S200.D1.HR2
	)
colnames(sauc21) <- c("S", c("Median (Q1, Q3)", "CR"))

sauc22 <- rbind.data.frame(
	F2.S70.D2.HR2, 
	F2.S200.D2.HR2
	)
colnames(sauc22) <- c("S", c("Median (Q1, Q3)", "CR"))


tab <- rbind(
  cbind(sauc11, sauc21), 
  cbind(sauc12, sauc22))

medq <- tab[,-c(1,4)]
S <- tab[,1]
Patients <- c("50-150", rep("", 13), "50-300", rep("", 13))
Methods <- rep(c(
  "HZ$_P$", 
  "HZ$_O$","Prop$_{(0.7)}$",
  "HZ$_O$","Prop$_{(0.5)}$",
  "HZ$_O$","Prop$_{(0.3)}$"),4)
P <- rep(c("", "0.7", "", "0.5", "", "0.3", ""),4)
tab1 <- cbind(
  Patients, S, P, Methods, medq
)
  
colnames(tab1) <- c("Patients","S", "$p$", "Methods", 
                    "Median (Q1, Q3)", "CR", "Median (Q1, Q3)", "CR")
rownames(tab1) <- NULL

if (save.tex) sink("TB-SAUC-UNIF.tex")
tab1 %>%
  kbl(
    caption="Summary of the estimated SAUC(2) when the true censoring is distributed as $U(1,4)$, but a misspecified exponential distribution is fitted.",
    format = "latex",
    longtable = F, 
    booktabs = T,
    align = "r",
    position = "!htb",
    linesep = c(rep('',6), '\\addlinespace'),
    escape = FALSE,
    label = "tab1",) %>%
  add_header_above(c(rep("",4), "Biomarker1"=2, "Biomarker2"=2),escape = FALSE) %>%
  footnote(general = ftn, 
   escape = FALSE, 
			threeparttable = TRUE,  
			general_title = "")
if (save.tex) sink()

```

